%%Put in another file just to handle everything easily.


%\begin{enumerate}

%3 cases: browsing courses (Ie, not necessarily a student), building a schedule, creating an account,

%\item Browsing courses: \\

\subsection*{Browsing Courses}
%
%
%who:   Anyone interested in the courses offered by University of Calgary.
%what:  Course list.
%why:   Has detailed information, provided in a c
  %UofC calendar - no time information.
  %Ours: Has a powerful search, for dept, course number, and course name. %May not be entirely true.
%how:   One visits our page and searches for interesting topics by name, courses in particular, or just simply clicks things.
%
Anyone interested in the courses offered by the University of Calgary, would navigate to our website to evaluate potential classes. They would then search for preferred courses by topic, department, course numbers, or course names. Alternatively one could browse the convenient side-bar for a complete listing. As they select courses, the course info, availability and other information appears in the center of the screen.

\subsection*{Building Schedule}
%\item Building Schedule
%Who:   Anyone interested in attending the University of Calgary.
%what:  Course List and Schedule builder.
%When:  When the data is available!
%why:   Easily build schedules. Easy to enroll via these schedules.
%how:
%
Any Students or Perspective students getting organized for the upcoming semesters, would navigate to our website to construct a class schedule. Powered by the same technology of the dauwtrappen course list, one can find courses and add it to the schedule's selected courses. On this list the user is provided a listing of class times for each section of the class, which they can then select the times they want. If a mistake was made, simply clicking the thing again... Once the user has the schedule to their liking, there are course numbers provided such that the user will be able to use these numbers to enroll directly in those classes via the my.ucalgary.ca Enrollment: add


\subsection*{Login System}
%\item Login System
%Who:   Anyone interested in attending the University of Calgary.
%what:  An account for our system.
%why:   Used to self-organize courses, and curate your own schedules. //Not yet fully implemented.
%how:   Create an account, Verify Account, login!
%

Any new students, prospective students, or returning students, may use the login/account system to curate their own schedules, and checkup on their own interested courses. They would accomplish this by creating an account, (which adds them to the database), and verifying their email. From then on, they are free to login, and see any personalized data sets.
%\end{enumerate}
